R Notebook

### 2022-02-11 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd

```{r}

colnames(smugDnkIdx_df)

head(smugDnkIdx_df, n=10)

head(smugDnkIdx_df, n=10)

@@

> dim() smugDnkIdx_df
>
> rows: 785
>
> columns: 4
>
> column names: "X2" "X3" "X5" "X6"

-   *need to rename column names to something
    memorable*

    ```{r}

    # example of melt function
    library(reshape)

    mdata <- 
      melt(smugDnkIdx_df,
           id=c(
             "id",
             "time")
           )
    ```

1.  *Identify and describe content of nodes and
    links,*

-   each of the 16 Florentine Family Names
    represent a Node in the network.

```{r Colnames}

@@

2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

@@

```{r Dimmentions, echo=TRUE}

  dim(smugDnkIdx_df)

>>>>

#
## Basic R: Import & Clean Data
```{r Import }
library(tidyr)
library(readr)

smugCovIdx <- read_csv("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA-Data/index-by_name-Smuggler_Cove-cocktail_recipies.csv", 
                       col_names = FALSE, 
                       col_types = cols(X1 = col_skip(), 
                                                        X4 = col_skip()))
```

```{r & Clean Data}
      # Drop NA rows
smugCovIdx <- na.omit(smugCovIdx)

# DATA Cleaning

#     Extract variables
#####
library(stringr)
          # extract first word of the column, adds values in new Column at the end of DF

                    #1st pastIt
passIt <- smugCovIdx

                    #2nd passIt
passIt$substring_first <-     
  str_extract(
    passIt$X5,
    "(\\w+)")

#####

#####
#     Drop it like...
#####
      # DROP COLUMNS FROM DATA FRAME

                      #3rd PassIt
passIt = subset(passIt, 
                       select = -c(3)
                       )
#####

#####
#     Give Variables a human name
#####

# rename column names with human language

                      # Return it
smugCovIdx <- passIt

names(smugCovIdx )[1] <- "dnkName"
names(smugCovIdx )[2] <- "dnkIng"
names(smugCovIdx )[3] <- "dnkCode"   
names(smugCovIdx )[4] <- "classIng"

@@

## Basic R: Brief Dataset Description
```{r Identify critical features of data:, echo=FALSE}

dim(smugCovIdx)

colnames(smugCovIdx)

summary(smugCovIdx)

@@

# Network: Creating network Data

# Network: Describe Network Data
## 1.  *Identify and describe content of nodes and
    links,*

##2.  *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

@@
